Automated Program Verification and Synthesis of Embedded \& Cyber-Physical Systems: Advances and Challenges

### 2018-02-23 paper.tex
added section about IC3
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\usepackage{booktabs} % For formal tables
% \usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{listings}
\usepackage{hyperref}	
\usepackage{afterpage}
\usepackage{graphicx}
\usepackage[caption=false]{subfig}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{epstopdf}
\usepackage{xcolor,colortbl}
% \usepackage{cite}
\newtheorem{mydef}{Definition}
\usepackage{multirow}
\usepackage{xspace}
\usepackage[ruled]{algorithm2e} % For algorithms
\renewcommand{\algorithmcfname}{ALGORITHM}
\SetAlFnt{\small}
\SetAlCapFnt{\small}
\SetAlCapNameFnt{\small}
\SetAlCapHSkip{0pt}
\IncMargin{-\parindent}

@@

\lstset{language=C,basicstyle=\small}
\lstset{numbers=left, numberstyle=\tiny, stepnumber=1, numbersep=5pt}
\lstset{tabsize=2}
\lstset{firstnumber=1}
\lstset{frame=single}
\lstset{
  language={C},
  morekeywords={assert,stdio,math,printf,assume,then,end-if,end,input,output}
}

@@

For instance, consider the C-code fragment shown in Figure~\ref{figure:inductive-invariant}. If we consider the IEEE floating-point standard (IEEE 754)~\cite{4610935,Goldberg91whatevery}, then  the loop invariant $x>0$ holds initially and after each iteration; actually, $x$ tends to infinity after $128$ iterations. Nonetheless, this invariant is not inductive, given that $x>0$ before an initial iteration does not ensure that $x>0$ after each iteration; if we initially have $x=0.9$, then $x<0$ after the fourth iteration. As a consequence, even if invariant generation procedures successfully compute such assertions, which are indeed invariant, those must be inductive, so that \textit{k}-induction verifiers can automatically prove program correctness. In this specific example, an inductive invariant would be $x>1$, given that if $x>1$ before the initial iteration, then also $x>1$ after \textit{k} iterations.
%
\begin{figure}[h]
\centering
\begin{minipage}{0.45\textwidth}
\begin{lstlisting}[basicstyle=\footnotesize]
#include <assert.h>
int main(void) {
 float x=2;
 while (1) {
   x = ((2*x) - 1);
 }
 return 0;
}
\end{lstlisting}
\end{minipage}
\caption{Motivating example for inductive invariants.}
\label{figure:inductive-invariant}
\end{figure}

@@

\textcolor{blue}{The application of the \textit{k}-induction method is gaining popularity in the software verification community. Bradley {\it et al.} introduced  ``property-based reachability'' (or IC$3$) procedure for the safety verification of systems~\cite{Bradley12,Bradley13}; the authors have shown that IC$3$ can scale on certain benchmarks, where \textit{k}-induction fails to succeed.}

>>>>

\usepackage{booktabs} % For formal tables
% \usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{listings}
\usepackage{hyperref}	
\usepackage{afterpage}
\usepackage{graphicx}
\usepackage[caption=false]{subfig}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{centernot}
\usepackage{epstopdf}
\usepackage{xcolor,colortbl}
% \usepackage{cite}
\newtheorem{mydef}{Definition}
\usepackage{multirow}
\usepackage{xspace}
\usepackage[ruled]{algorithm2e} % For algorithms
\renewcommand{\algorithmcfname}{ALGORITHM}
\SetAlFnt{\small}
\SetAlCapFnt{\small}
\SetAlCapNameFnt{\small}
\SetAlCapHSkip{0pt}
\IncMargin{-\parindent}

@@

\lstset{language=C,basicstyle=\small}
\lstset{numbers=left, numberstyle=\tiny, stepnumber=1, numbersep=5pt}
\lstset{tabsize=2}
\lstset{firstnumber=1}
\lstset{frame=single}
\lstset{
  language={C},
  morekeywords={stdio,math,printf,assume,then,end-if,end,input,output}
}

@@

For instance, consider the C-code fragment shown in Figure~\ref{figure:inductive-invariant}. The star-notation indicates nondeterminism. If we consider the IEEE floating-point standard (IEEE 754)~\cite{4610935,Goldberg91whatevery}, then  the invariant $x>0$ holds initially and after each iteration; actually, $x$ tends to infinity after $128$ iterations. Nonetheless, this invariant is not inductive, given that $x>0$ before an initial iteration does not ensure that $x>0$ after each iteration; if we initially have $x=0.9$, then $x<0$ after the fourth iteration. As a consequence, even if invariant generation procedures successfully compute such assertions, which are indeed invariant, those must be inductive, so that \textit{k}-induction verifiers can automatically prove program correctness. In this specific example, an inductive invariant would be $x>1$, given that if $x>1$ before the initial iteration, then also $x>1$ after \textit{k} iterations.
%
\begin{figure}[h]
\centering
\begin{minipage}{0.35\textwidth}
\begin{lstlisting}[basicstyle=\footnotesize]
#include <assert.h>
int main(void) {
 float x=*;
 while (1) {
   x = ((2*x) - 1);
 }
 return 0;
}
\end{lstlisting}
\end{minipage}
\caption{Motivating example for inductive invariants.}
\label{figure:inductive-invariant}
\end{figure}

@@

\textcolor{blue}{Bradley {\it et al.} introduced  ``property-based reachability'' (or IC$3$) procedure for the safety verification of systems~\cite{Bradley12,Bradley13}; the authors have shown that IC$3$ can scale on certain benchmarks, where \textit{k}-induction fails to succeed. In particular, the success of IC3 over \textit{k}-induction procedures is due to the ability of the former to guide the search for inductive instances with counterexamples to the inductiveness (CTIs) of the given property~\cite{Bradley18}. Consider again the C-code fragment shown in Figure~\ref{figure:inductive-invariant}, that $\rho : x > 0$ is an invariant.}

\begin{equation}
x > 0 \wedge x' = 2*x - 1 \centernot\implies x > 0. \nonumber
\end{equation}

\textcolor{blue}{In this specific example, a CTI returned by an SMT solver is $x=0$. If this state is not eliminated, then the invariant $\rho$ cannot be established. The generated inductive assertion should establish that the CTI $x=0$  is unreachable. If no such inductive assertion exists, then other CTIs can be examined instead ({\it e.g.}, $0.1$, $0.2$, $\dots$, $0.9$). As a result, the lemmas should be strong enough that consecutively revisiting a finite set of CTIs will eventually end up in an assertion, which is inductive relative to them, thus eliminating the CTI. In this example, the instance $x > 1$ ($a=1$, $b=0$) is inductive and eliminates all possible CTIs.}

\textcolor{blue}{Jovanovi\'{c} {\it et al.}~\cite{Jovanovic:2016:PK:3077629.3077648} present a reformulation of IC3, separating the reachability checking from the inductive reasoning. They further replace the regular induction algorithm by the \textit{k}-induction algorithm and show that it provides more concise invariants. The authors implemented the algorithm in the SALLY model checker using Yices2 to do a forward search and MathSAT5 to do a backward search. They showed that the new algorithm is able to solve a number of real-world benchmarks, at least as fast as other approaches.}
